Interval Probability for Fuzzy Quantum Theories

### 2016-05-12 prob.tex
prob.tex "Interval-valued probability measures" update comment...

There is however another more subtle source of unbounded computational
power in the experiment. We are assuming that we can always determine
with certainty whether a needle is crossing a line. But ``lines'' on
the the floor have thickness, their distance apart is not exactly
$\ell$. and the needles lengths are not all equal and are not all
absolutely equal to $\ell$. These perturbations make the events
``fuzzy.'' For example, instead of talking about the idealized event
that exactly $M$ needles cross lines which would require the most
expensive needles built to the most precise accuracy, laser precision
for drawing lines on the floor, and the most powerful microscopes to
determine if a needle does cross a line, we might instead talk about
the event that $M-\delta$ needles evidently cross lines and
$M+\delta'$ needles plausibly cross lines for some acceptable
approximations $\delta$ and $\delta'$. This fuzzy notion of events
leads us to consider intervals of probability reflecting the certainty
of the event and its plausibility. In another experiment with
$3204$ needles and the ratio $\frac{\ell}{h}=0.6$~\cite{DeMorgan1872}, 
there are $1213$ needles clearly crossed a line and $11$ ones
was close enough to plausibly be considered as crossing the line: we
would express the probability in this case as the interval
$\left[\frac{1213}{3204},\frac{1224}{3204}\right]$ expressing that we are
certain that the event has probability at least $\frac{1213}{3204}$ but it is possible that
it would have probability $\frac{1224}{3204}$.

@@

\yutsung{Set-valued is not a particular case of interval-valued probability.
In particular, the rule they respect are different. A real-valued
probability measure $\pmeas:\events\rightarrow[0,1]$ should satisfy
the following two rules:
\begin{enumerate}
\item $\pmeas(\Omega)=1$, and 
\item for a collection $E_{i}$ of pairwise disjoint events, $\pmeas(\bigcup_{i}E_{i})=\sum_{i}\pmeas(E_{i})$.
\end{enumerate}
When the range of $\pmeas$ is not only a real number, these conditions
cannot be both reserved. The set-valued probability measure preserves
Condition 2 and modifies Condition 1. The interval-valued probability
measure preserves Condition 1 and modifies Condition 2.

It seems hard to make a consistent story with the general set-valued
probability measure framework (except possible/impossible?), so we
just comment out set-valued probability measure here...}

>>>>

There is however another more subtle source of unbounded computational
power in the experiment. We are assuming that we can always determine
with certainty whether a needle is crossing a line. But ``lines'' on
the the floor have thickness, their distance apart is not exactly
$h$. and the needles lengths are not all equal and are not all
absolutely equal to $\ell$. These perturbations make the events
``fuzzy.'' For example, instead of talking about the idealized event
that exactly $M$ needles cross lines which would require the most
expensive needles built to the most precise accuracy, laser precision
for drawing lines on the floor, and the most powerful microscopes to
determine if a needle does cross a line, we might instead talk about
the event that $M-\delta$ needles evidently cross lines and
$M+\delta'$ needles plausibly cross lines for some acceptable
approximations $\delta$ and $\delta'$. This fuzzy notion of events
leads us to consider intervals of probability reflecting the certainty
of the event and its plausibility. In another experiment with
$3204$ needles and the ratio $\frac{\ell}{h}=0.6$~\cite{DeMorgan1872}, 
there are $1213$ needles clearly crossed a line and $11$ ones
was close enough to plausibly be considered as crossing the line: we
would express the probability in this case as the interval
$\left[\frac{1213}{3204},\frac{1224}{3204}\right]$ expressing that we are
certain that the event has probability at least $\frac{1213}{3204}$ but it is possible that
it would have probability $\frac{1224}{3204}$.

@@

\yutsung{Set-valued is not a particular case of interval-valued probability
because their rules are different. A set-valued probability measure
should satisfy: 
\begin{enumerate}
\item $1\in\pmeas(\Omega)$, and 
\item for a collection $E_{i}$ of pairwise disjoint events, $\pmeas(\bigcup_{i}E_{i})=\sum_{i}\pmeas(E_{i})$. 
\end{enumerate}
which are completely opposite to the interval-valued probability measures.

It seems hard to make a consistent story with the general set-valued
probability measure framework (maybe except possible/impossible?),
so we just comment out set-valued probability measure here...}
